---
title: "ExpectedDensityEtAl"
author: "Steven M. Goodreau"
date: "March 7, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ergm)
```

## Cross-sectional networks (ERGM parameters)

Define 
- $n$: # of nodes
- $e$: # of edges
- $y$: # of dyads
- $d$: density
- $m$: mean degree
- $\theta$: edges coefficient

We know:

- $y = \frac{n(n-1)}{2}$

- $d = \frac{e}{y} = \frac{2e}{n(n-1)}$

- $m = \frac{2e}{n} = d(n-1)$ 

- $\theta = ln(\frac{d}{1-d})$

```{r}
n <- 100
e <- 45
(y = n*(n-1)/2)
(d <- e/y)
(m = d*(n-1))
(theta <- log(d/(1-d)))
ergm(network.initialize(n, directed=FALSE)~edges, target.stats=e)$coef
```


## Dynamic networks (STERGM parameters)

Define 
- $n$: # of nodes
- $e$: # of edges
- $y$: # of dyads
- $d$: density
- $m$: mean degree
- $\theta^{+}$: edges coefficient, formation model
- $\theta^{-}$: edges coefficient, dissolution model
- $r$: mean relational duration
- $s$: dissolution probability per time step

As before:

- $y = \frac{n(n-1)}{2}$

- $d = \frac{e}{y} = \frac{2e}{n(n-1)}$

- $m = \frac{2e}{n} = d(n-1)$ 

But now:

- $r =   1/s$

- $\theta^{-} = ln\frac{1-s}{s}$ and 
$s = \frac{e^{\theta^{-}}}{1-e^{\theta^{-}}}$

But what about edges/density/mean degree as a function of the two $\theta$ values?  We know that at equilibrium, the expected number of edges forming at each time step will equal the expected nmber dissolving, or:

$es = (y-e)x$
$es = yx - ex$
$es + ex = yx$
$e=(s+x)=yx$
$e = y \frac{x}{s+x}$

# of edges = # of dyads * (form_prob)/ (form_prob + diss_prob)

$x = es/(y-e)$

form prob = edges*diss_prob / nonties


```{r formprob}
s <- 0.01
formprob <- e*s/(y-e)
formlogit <- log(formprob/(1-formprob))
stergm()

```
